Towards Correct Legion

### 2017-08-25 correctnesshpc/paper.tex
a few spelling/style fixes

In addition, recent work has shown that modular, composable formal
specifications enable formal correctness proofs for large software systems that
were previously unattainable \cite{?}. By integrating a formal specification
tightly with an implementation, one can achieve the highest levels of
confidence in code currently possible \cite{?}. For example, the Compcert
project implements an optimizing c compiler and proves it correct. The success
of Compcert in removing compiler bugs has been well documented. We will discuss
later how Compcert could be used in building verifiable HPC systems.

In HPC, programming models have become an increasingly important way to ensure
that code stays maintanable, performant, and portable \cite{?}. We claim that
these programming models provide a good target for formalization: any
correctness arguments can be leveraged by every program using the model. It is
exactly this kind of modularization of proofs that has been so successful in
proving programs correct \cite{?}.

@@

By partitioning regions into \emph{subregions}, and tracking \emph{privileges}, 
Legion is able to ensure that certain code won't interfere or alias, and can
therefor be safely, at least with respect to those memory regions, run in
parallel. This theory has been put into practice to impressive effect, and has
been shown to scale both within a node and between \cite{legionpapers}. That
said, there are still challenges subtle bugs that occasionally show up in the
implementation. It is possible that these kinds of bugs could manifest
themselves in ways that would lead to incorrect conclusions when informing
major decisions, something we'd generally like to avoid. One goal of this paper
is to move towards formally and systematically removing \emph{all} bugs from
the programming model, giving everyone who uses is far more certainty that 
their code is correct.

@@

Specifications come in a wide range of formats. Many, like the OpenMP
specification, are very informal, primarily consisting of english descriptions
of how different constructs should behave \cite{openmp}. Others, like Legion's,
are written by hand in the using standard notation for logical relations, etc.
For this paper, when we refer to a \emph{formal} specification, we are
referring to a specification defined in a formal logic, like Coq.

@@

All of these issues are addressable given enough time and effort. Some offer
a nice opportunity for modularity within the tasking formalization. For example, 
ordering tasks based on dependencies of values is common accross all tasking
systems \cite{cilk, hpx}, and is likely a sort of sub-semantics that they could
all share, reducing proof burden across different runtimes.

>>>>

In addition, recent work has shown that modular, composable formal
specifications enable formal correctness proofs for large software systems that
were previously unattainable \cite{?}. By integrating a formal specification
tightly with an implementation, one can achieve the highest levels of
confidence in code currently possible \cite{?}. For example, the Compcert
project implements an optimizing C compiler and proves it correct. The success
of Compcert in removing compiler bugs has been well documented. We will discuss
later how Compcert could be used in building verifiable HPC systems.

In HPC, programming models have become an increasingly important way to ensure
that code stays maintainable, performant, and portable \cite{?}. We claim that
these programming models provide a good target for formalization: any
correctness arguments can be leveraged by every program using the model. It is
exactly this kind of modularization of proofs that has been so successful in
proving programs correct \cite{?}.

@@

By partitioning regions into \emph{subregions}, and tracking \emph{privileges}, 
Legion is able to ensure that certain code won't interfere or alias, and can
therefore be safely, at least with respect to those memory regions, run in
parallel. This theory has been put into practice to impressive effect, and has
been shown to scale both within a node and between \cite{legionpapers}. That
said, there are still challenges --subtle bugs that occasionally show up in the
implementation. It is possible that these kinds of bugs could manifest
themselves in ways that would lead to incorrect conclusions when informing
major decisions, something we'd generally like to avoid. One goal of this paper
is to move towards formally and systematically removing \emph{all} bugs from
the programming model, giving everyone who uses is far more certainty that 
their code is correct.

@@

Specifications come in a wide range of formats. Many, like the OpenMP
specification, are very informal, primarily consisting of english descriptions
of how different constructs should behave \cite{openmp}. Others, like Legion's,
are written by hand in the using standard notation for logical relations, etc.
For this paper, when we refer to a \emph{formal} specification, we are
referring to a specification defined in a formal logic, eg. Coq.

@@

All of these issues are addressable given enough time and effort. Some offer
a nice opportunity for modularity within the tasking formalization. For example, 
ordering tasks based on dependencies of values is common accross all tasking
systems \cite{cilk, hpx}, and is likely a sort of sub-semantics that they could
all share, reducing proof burden across different run-times.
